### 2022-05-30 README.Rmd
added zenodo badge

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/MartinHinz/bayesian.demographic.reconstruction.2022/master?urlpath=rstudio)

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/MartinHinz/bayesian.demographic.reconstruction.2022/master?urlpath=rstudio) [![DOI](https://zenodo.org/badge/477622472.svg)](https://zenodo.org/badge/latestdoi/477622472)
